FIXME

### 2013-09-23 writeups/proposal/proposal.tex
foo
Former-commit-id: dbae64aa0af5e242146aafca447fe3df2b3e5513 [formerly f40ec5ac8e5c9873ed2c8709838e6775dcd27d43]
Former-commit-id: 0ae74501bf620ef9dc4c1e44718b0fc82c4946a5
spell checked
Former-commit-id: bc27cf4a681892758c1b954e6710c74111fab7d9 [formerly 617e8fbab83471cee84a4d90efcc24eead05360f]
Former-commit-id: de5a1e16e71560fe047dc10948233971d2df65bc

TODO: Motivation

Social media sites such as Twitter, Facebook, StackOverflow, Google+, and Yelp, are composed almost entirely of human-generated content.
The amount of human-generated content on these sites is staggering, and continues to grow.
Users of Twitter's microblogging service, for example, generate half a billion tweets per day \parencite{TwitterReport2012}.
However, a single user of a social media site is most likely interested in only a small fragment of this large amount of information.
One general question to support the the user in this domain is:
How can we quickly and effectively connect users to the content that they care about?

@@

So how can we ensure that users are connected to the information streams that they care most about?
One promising approach is to model and predict the user's goals when using and searching these social media sites \parencite{Rose2004}.
If we have a better understanding of a user's goals, then we can tailor the information streams provided to the ones that are most inline with these goals.
For example, Twitter might suggest other users and hashtags for the user to follow, Facebook could suggest pages to like, Yelp could recommend businesses to check out, etc.
Researchers are currently looking for ways to automate the goal-identification task for more general search queries like those generated for Google \parencites{Jansen2008}{Lee2005}.

@@

We will compare these two memory systems across two domains where users generate tags for posts: Twitter and StackOverflow.
Twitter is a micro-blogging service where users create 140 character tweets and broadcast those messages out to the users who follow their posts.
A user is free to annotate important concepts or words in the tweet by preceding words with hashtags ``\#''.
User-created hashtags on Twitter are embedded into the tweet, and can be used to connect the tweet to other tweets about the same topic through common hashtag use.
After the tweet is created the hashtags become hyperlinks, and if clicked on will take a user to a summary feed of all of the tweets across Twitter that have used that hashtag.
Some recent and often-used hashtags for Twitter are \emph{\#photography}, \emph{\#startup}, \emph{\#4change}, \emph{\#android}, and \emph{\#solar}.

@@

% FIXME: Use a different example figure
\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{visPost-2977094-screen-crop.pdf}}}
  \caption{Example post on stackoverflow.com}
  \label{figSOExample}
\end{figure}

@@

These two datasets were chosen because the content of the human-generated content is quite different between them, and we are interested in retrieval models that generalize across different task domains.
However, they are also quite similar on several accounts:
Both domains have emassed large amounts of user-generated content, users generate tags for posts when creating content on the site, and the user data from the datasets are publicly available for analysis.

Also, studying user-based tag generation on these sites is a relevant task domain.
Models that can accuratly predict the tags that users will generate on Twitter and StackOverflow can be used as the foundation for recommendations systems on these very popular sites.
These systems can help newer users by recommending proper tags for their newest content.
On the StackOverflow site for example, experts often subscribe to specific hashtags that interest them, and receive a daily digest of posts that are tagged with those hashtags.
Helping the user properly tag posts on StackOverflow ensures that right community sees the post, which greatly increases the chance that the question on the post will be answered quickly and correctly.
For Twitter, hashtags represent streams of information that are possibly interesting to the user.
Having a recommendation system that can suggest relevant hashtags to the user provides a way for the user to connect to and discover new information streams.

@@

Prior research has examined the growth and decay cycle of hashtag use across users \parencite{Tsur2012}.
However, much less is known about hashtag lifetime within a single user.
It may not be the case that a hashtag's lifecycle for a single user matches the lifecycle across users.
Further, modeling a hashtag's life within users is much more applicable to hashtag prediction, since that model can be directly incorporated into the a specific user's prior likelihood of hashtag use.
So we will characterize the hashtag growth and decay cycle within users.
The expectation is that this cycle will match ACT-R's decay rate used in the declarative memory system to compute a particular memory item's prior.
This decay rate equation formalizes how recency and frequency of hashtag use relate to the prior probability that a hashtag will be retrieved.

@@

The end goal of this work is to identify a memory retrieval model that can suggest relevant hashtags to users when they wish to retrieve one.
These hashtags should be customized to their specific interests and relevant to the content of the post that they are currently creating.
This will undoubtably require a combination of two primary model components:
[1] A user's prior likelihood of choosing a particular hashtag, given their prievously-generated content, and [2] the likelihood that a particular hashtag is related to the context of the post being generated.

A user's prior hashtag use will be an essential model component for domains such as Twitter, where the number of possible hashtags is practically infinite.
In these domains, the model can utilize a user's prior hashtag use as a way to prune the infinite space of possible hashtags, and generate a much smaller and more manageable set for prediction.
However, not only should the model properly take into account a user's prior hashtag use, but it should also generate new hashtag predictions when a user is most likely choosing a hashtag they have never used before.
Calibrating the models to properly balance this exploitation of prior hashtag use vs. exploration of new hashtags will be a primary resaerch focus.
The end goal is to have a model that can properly balance the user's prior tag with the contextual cues in the post in order to generate an accurate prediciton.

@@

A model that predicts a user-chosen hashtag is a specific type of the more general recommendatino systems.
These systems have grown in need with the growth of the web.
Users on a site need quick access to specific pieces of information, and the site contains much more information than they can process or care about.
Recommendation systems are used to tailor the information presented to what is most relevant to the user \parencite{Pazzani2007}.

@@

Recommendation systems based on the content of user-generated posts have been successfull in recommending people on Twitter for a user to follow.
\textcite{Hannon2010} built a Twitter follower recommendation system by creating a profile of each user based on the words they used in previous posts.
The recommendation system would then suggest other Twitter users to follow that had similar profiles to a particular user.
The profiles were created by generating a word frequency matrix of words x (user + followers + followees), and then providing that matrix as input into the Lucine text search engine framework.
When the system needed to recommend a set of individuals for a user to follow, it would take all of the words used in posts from that user to construct a search query to be provided to Lucine.
That search query would return the most likely users that share similar words in posts within their twitter network with the words provided in the query.
Using this simple technique based on a standard text search engine allowed the recommendation system to accurately predict the people that a particular user will follow at 25\% accuracy.

@@

\textcite{Efron2010} showed how hashtags might be used as a type of recommendation system for Twitter.
Users constructed a query of text that represented a search for a topic that they were interested in.
The system then retrieved the most likely hashtags that were associated with that search query.
The model is based on building a word co-occurance matrix of words x hashtags, and then uses that matrix to assign a similarity score for each hashtag when provided with a search query.
Participants graded how relevant the hashtags returned were to each search query.
The results suggest that hashtags contain useful information that help classify the gist of a post. 
Although this model does not predict hashtags directly when composing a tweet, a model like this could certainly be tailored for that purpose.

@@

\textcite{Kuo2011} was the first to model tag use for StackOverflow posts.
His set of models were originally designed for next-word prediction for large text document collections.
In order to structure the models to work for StackOverflow tag prediction, the models would request the most-likely next word after a user generated a post, and restrict the space of possible words to only tags.
He tested the set of next-word predictino models to generate predictions for the most likely tags that a user would choose when asking a question on the site.
Interestingly, the Bayesian co-occurrance model outperformed the more complicated and computatinoally expensive Singular Value Decomposition and K-nearest-neighbors models.
This model can accurately predict a user-chosen tag at 47\% accuracy.

\textcite{Stanley2013} also modeled a user's chosen tags for a post on the StackOverflow site.
The model was based on ACT-R's declarative memory retrieval theory, which at the core is also a Bayesian co-occurrance model.
However, this model scaled much better than the co-occurrance model presented in \textcite{Kuo2011}.
Because of this, 100 times more posts were used to build the co-occurrance matrix (\num{1000000} versus \num{10000}), which significantly increased the model's performance.
After scaling up the model, this model can successfully predict a user's tag for a post at 65\% accuracy.
It is interesting that in both research papers the best performing model was based on a Bayesian co-occurrance framework, since that is precisely the framework from which ACT-R's declarative memory system is built.
This suggests that more cognitively-plausible memory retrieval models may outperform more general machine-learning approaches in this particular task domain:
predictng the user-chosen tags for human-generated content on social media sites.

A tag suggestion tool has also been deployed for the tex.stackexchange.org site. \parencite{LatexTags2013}
Both the \LaTeX site and StackOverflow are part of the broader StackExchange network of question and answer sites, and they provide the same user interface and workflow when asking questions.
Once a user has created a question on the Latex site, the site provides subdued text of suggested tags in the text field where the user fills in the tags to associate with the question.
The post author is not forced to use the suggested tags, and is free to choose tags from them or tags not represented in the suggested set.

@@

The hashtag recommendation system deployed for the Google+ micro-blogging service is probably the most ambitious model of user-created hashtags to date \parencite{GoogleKeynote2013}.
The user interface for this recommenation system for an example Google+ post is shown in Figure \ref{figGoogle+Hashtags}.

\begin{figure}[!htbp]
  \scalebox{.4}{\resizebox{\linewidth}{!}{\includegraphics{google+HashtagExample-crop.pdf}}}
  \caption{Example post on google+. The system recommended \emph{\#SFGiants} and \emph{\#BusterPosey} as hashtags for the user-generated post}
  \label{figGoogle+Hashtags}
\end{figure}

@@

Several other models have taken a tweet-centered approach to hashtag prediction, where suggested hashtags are collected from hashtags used from similar tweets.
\textcites{Li2011, Zangerle2011, Kywe2012} all store a content vector for each tweet, and then compute a word co-occurence-based similarity score between a composed tweet and the rest of the tweets in the database.
\textcites{Zangerle2011, Kywe2012} use the Apache Lucine infrastructure to compute the similarity score, while \textcite{Li2011} uses a custom similarity score derived from the WordNet database to compute similarites.
Regardless of the method to compute the similarity between tweets, each method collects the hashtags used from a set of the most similar tweets, then ranks the set, and presents the top 5-10 hashtags to the user.

This tweet-centered approach is quite different than the hashtag-centered approach presented in \textcite{Mazzia2009}.
With a hashtag-centered approach, a direct association is built between the words in a tweet and hashtags that occur in tweets.
With a tweet-centered approach, that association between words and hashtags is indirect:
The relationship is built between a tweet and its content, and then similar tweets are assumed to use similar hashtags.
One problem with the tweet-centered approach is that the storage size grows with the number of tweets, as a vector representatino of the content in each tweet has to be maintained to later compute tweet similarity.
The storage size for a hashtag-centered approach grows with the number of hashtags, but it seems reasonable that this will grow slower than the number of tweets and asymptote after collecting a large sample of tweets.
So from the perspective of efficient information storage and retrieval, it seems more likely that the hashtag-centered approach used in \textcite{Mazzia2009} will scale as Twitter grows in size and use.

\textcite{Kywe2012} also customized their tag predictino model to the user's past hashtag use, and was one of the first to do so when developing a hashtag-prediction model for Twitter.
The set of recommended hashtags was the union of hashtags used in similar tweets and hashtags used by similar users.
This was done by storing a content vector of hshtag use for each user (user-centered approach) alongside the content vectors of hashtag use for each tweet (tweet-centered approach).
To generate recommended hashtags, the model would return the top-ranked hashtags from the hashtags used in 0-50 similar tweets and 0-4 similar users.
Prediction accuracy improved when the model combined recommendations based on hashtags in both similar tweets and the top few similar users compared to basing recommendations on similar tweets alone.

A topics-based approach was used by \textcite{Godin2013}, where the model predicted the most likely set of topics that were associated with a tweet, and tested if these topics matched the tweet by using human raters.
The latent topics for the colleciton of tweets were generated using a Latent Dirichlet Allocation statistical methodology.
This is similar to singular value decomposition in that the most likely hidden dimensions (i.e., topics) of the data are discovered by searching for reduced representations of the data that cover most of the variance. 
Human graders rated how well the models generated topics for a tweet related to the content in the tweet.
The LDA model performed well, and generated relevant topics.

@@

Although recent work has been done to model human tagging on the StackOverflow site, to our knowledge no vector-based holographic memory model has been tested or used.
We are curious to see the prediction difference between a vector-based models and current co-occurrance models on the StackOverflow dataset.
Both types of models are neurologically plausible, and both have been successfully incorporated as the declarative memory component of the ACT-R cognitive architecture \parencite{Rutledge2007}. 
Given that the Bayesian cognitively-plausible models have done so well to predict tag use on StackOverflow, we are curious to see how a cognitively-plausible vector-based model performs at the task.

Also, a vector-based retrieval model has not yet been tested on Twitter.
One of the advantages of vector-based models is that word order can be easily incorporated into the single co-occurrence representation \parencite{Jones2007}.
It seems quite likely that the few words used just before a hashtag embedded in a tweet will be highly predictive of the hashtag chosen.
To our knowledge, only bag-of-words models have been tested on Twitter to predict hashtags, where co-occurrance between words and hashtags are computed independently from where the word is located in the tweet.
It will be interesting to see how much (if at all) accuracy improves when incorporating word-order information into the model.

There has been a mix of co-occurrence and latent-based models created to predict hashtags use on Twitter, and the results are encouraging.
However, there has been very little research on how a specific user's past hashtag use should influence the model's prediction when that user is composing a tweet.
\textcite{Kywe2012} did take a user-centered view with their model, but the hashtags predicted by the user and content were analyzed separately and then the top from each group were combined for prediction.
The ACT-R declarative memory retrieval theory shows how past user behavior and current context combine to produce the most likely retrieval.
Each component is summed together to generate a total activation, and then the likelihodd of chunks are ranked by that summed activation.
This technique allows for a more natural combination of the two components, where weights can be assigned to each component depending on how strongly each term predicts performance.
This type of weighted additive model that combines past user behavior and current tweet context to predict the most likely hashtags has not yet been explored for Twitter.

@@

ACT-R \parencite{Anderson2004} is a cognitive architecture that formalizes how each cognitive process of the brain (e.g., memory, learning, visual and motor) interacts to produce behavior.
The declarative memory system is a component of that architecture that models the timing, learning, and forgetting processes that make up long-term declarative memory retrieval.
The equations that make up this system can be described through a rational analysis of long-term memory retrieval.
That is, given the task of retrieving a chunk of information from long-term declarative memory,
the current context (i.e., external and internal environment state), and past experience (i.e., prior memories and exposure), 
what is the optimal behavior (i.e., the optimal chunk to retrieve from memory)?
Using Bayesian reasoning, each chunk of information in declarative memory can be assigned a prior likilihood of being retrieved again, given the prior number of times it has been needed.
Those prior probabilities for each chunk are then adjusted for the current context, so that the posterior probabilities represent the likilihood that a chunk is needed, given prior odds and current environment state.

@@

For some domains, it is reasonable to assume that the base-level activations of each chunk within a particualar window of interest are stable, and do not change within that window.
Programming-language popularity over the past few years is a reasonable example of this.
Although the popularity of various programming languages has certainly changed slightly over the past few years (.e.g, \emph{closure}'s growth), it is not the case that the changes have been drastic.
\emph{C\#}, \emph{Python}, and \emph{Java} are still a few of the most popular languages, \emph{Common Lisp} has not gained or lost much ground in popularity over the past few years, etc.

@@

Strength of association ($S_{ji}$) reflects the amount of log odds adjustment to the activation of a chunk, given the current context (i.e., external environment and internal state).
Context for the StackOverflow domain for example, can be represented as each word in the title and body of a post.
Context for the Twitter domain would be the words in a Tweet.
Association strenght between a chunk in memory and a single contextual element can be computed directly by calculating its context-adjusted odds ratio:
The likelihood a chunk occurred with the current context ($p(i|j)$) over the likeihood that the chunk occured in any of the other contexts ($p(i|\overline{j})$).
For large datasets, the likelihood that a chunk occurs in any particular context reaches near-zero values ($p(j) \Rightarrow 0$).
So it can be assumed that the likelihood that a chunk occurs in any context but one ($p(i|\overline{j})$) is equivalent to the likelihood that a chunk occurs in any context ($p(i)$).
This assumption has been both mentioned and used when deriving the $S_{ji}$ equation \parencite{Anderson1989}, as well as in recent research working with large-scale datasets \parencite{Stanley2013}.

Using this assumption for large datasets, the interpretation of the context-adusted odds ratio becomes much simpler.
If this ratio for a particular tag and context chunk is greater than one, then the log is positive, which means that this context has been observed more often with this tag than in general.
If this ratio is less than one, then the log is negative, which provides a negative adjustment of total activation since this context has been observed more often in general than with this particular tag.

@@

The majority of tag-recommendation systems use some measure of word pair associations to compute the likelihood of a tag, given current context.
It is important that this measure scales well enough to handle the sheer volume of information present in online social media datasets.
Large-scale social media datasets such as StackOverflow and Twitter contain on the order of millions to hundreds of millions of unique word pair associations between terms and tags.
If one wants to capitilize on all of the information present in the database to build the most accurate measure of relatedness between words and tags, then the association measure used must scale to this large size.

@@

The SNIF-ACT framework is also based on the large-scale version of $S_{ji}$, and scales well when working with a large-scale search query database for internet search \parencites{Fu2007,Pirolli2003}.
The $S_{ji}$ values were based on a 118GB local database of 10 million pages of the Stanford Webbase Project \parencite{Farahat2004}.
So this implementation did not fit into RAM, but a spinning-disk database implementation still scaled well enough for reasonably fast retrieval times for $S_{ji}$ values.

@@

A formal description of the modified ACT-R Bayesian model from \textcite{Stanley2013} is included in Table \ref{tabModACTRModel}.
The activation of each tag ($A_{i}$) is a function of four components:
That tag's base level activation ($B_{i}$), contextual activation for the words in the title, activation for words in the body, and an offset term ($O$).
This model has been modified from the standard ACT-R model (Table \ref{tabACT-RModel}) in three ways:
Two separate contextual compoennts were used (words in title and body of post), an offset term was added, and an entropy metric was used to compute the attential weight ($W_{j}$).

>>>>

Social media sites such as Twitter, Facebook, StackOverflow, Google+, and Yelp, are composed almost entirely of human-generated content.
The amount of human-generated content on these sites is staggering, and continues to grow.
Users of Twitter's microblogging service, for example, generate half a billion tweets per day \parencite{TwitterReport2012}.
However, a single user of a social media site is most likely interested in only a small fragment of this large amount of information.
One general question to support the user in this domain is:
How can we quickly and effectively connect users to the content that they care about?

@@

So how can we ensure that users are connected to the information streams that they care most about?
One promising approach is to model and predict the user's goals when using and searching these social media sites \parencite{Rose2004}.
If we have a better understanding of a user's goals, then we can tailor the information streams provided to the ones that are most in line with these goals.
For example, Twitter might suggest other users and hashtags for the user to follow, Facebook could suggest pages to like, Yelp could recommend businesses to check out, etc.
Researchers are currently looking for ways to automate the goal-identification task for more general search queries like those generated for Google \parencites{Jansen2008}{Lee2005}.

@@

We will compare these two memory systems across two domains where users generate tags for posts: Twitter and StackOverflow.
Twitter is a microblogging service where users create 140 character tweets and broadcast those messages out to the users who follow their posts.
A user is free to annotate important concepts or words in the tweet by preceding words with hashtags ``\#''.
User-created hashtags on Twitter are embedded into the tweet, and can be used to connect the tweet to other tweets about the same topic through common hashtag use.
After the tweet is created the hashtags become hyperlinks, and if clicked on will take a user to a summary feed of all of the tweets across Twitter that have used that hashtag.
Some recent and often-used hashtags for Twitter are \emph{\#photography}, \emph{\#startup}, \emph{\#4change}, \emph{\#android}, and \emph{\#solar}.

@@

% FIXME: Use a different example figure
\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{stackoverflowPostExample1-crop.pdf}}}
  \caption{Example post on stackoverflow.com}
  \label{figSOExample}
\end{figure}

@@

These two datasets were chosen because the content of the human-generated content is quite different between them, and we are interested in retrieval models that generalize across different task domains.
However, they are also quite similar on several accounts:
Both domains have amassed large amounts of user-generated content, users generate tags for posts when creating content on the site, and the user data from the datasets are publicly available for analysis.

Also, studying user-based tag generation on these sites is a relevant task domain.
Models that can accurately predict the tags that users will generate on Twitter and StackOverflow can be used as the foundation for recommendations systems on these very popular sites.
These systems can help newer users by recommending proper tags for their newest content.
On the StackOverflow site for example, experts often subscribe to specific hashtags that interest them, and receive a daily digest of posts that are tagged with those hashtags.
Helping the user properly tag posts on StackOverflow ensures that right community sees the post, which greatly increases the chance that the question on the post will be answered quickly and correctly.
For Twitter, hashtags represent streams of information that are possibly interesting to the user.
Having a recommendation system that can suggest relevant hashtags to the user provides a way for the user to connect to and discover new information streams.

@@

Prior research has examined the growth and decay cycle of hashtag use across users \parencite{Tsur2012}.
However, much less is known about hashtag lifetime within a single user.
It may not be the case that a hashtag's life cycle for a single user matches the life cycle across users.
Further, modeling a hashtag's life within users is much more applicable to hashtag prediction, since that model can be directly incorporated into a specific user's prior likelihood of hashtag use.
So we will characterize the hashtag growth and decay cycle within users.
The expectation is that this cycle will match ACT-R's decay rate used in the declarative memory system to compute a particular memory item's prior.
This decay rate equation formalizes how recency and frequency of hashtag use relate to the prior probability that a hashtag will be retrieved.

@@

The end goal of this work is to identify a memory retrieval model that can suggest relevant hashtags to users when they wish to retrieve one.
These hashtags should be customized to their specific interests and relevant to the content of the post that they are currently creating.
This will undoubtedly require a combination of two primary model components:
[1] A user's prior likelihood of choosing a particular hashtag, given their previously-generated content, and [2] the likelihood that a particular hashtag is related to the context of the post being generated.

A user's prior hashtag use will be an essential model component for domains such as Twitter, where the number of possible hashtags is practically infinite.
In these domains, the model can utilize a user's prior hashtag use as a way to prune the infinite space of possible hashtags, and generate a much smaller and more manageable set for prediction.
However, not only should the model properly take into account a user's prior hashtag use, but it should also generate new hashtag predictions when a user is most likely choosing a hashtag they have never used before.
Calibrating the models to properly balance this exploitation of prior hashtag use versus exploration of new hashtags will be a primary research focus.
The end goal is to have a model that can properly balance the user's prior tag with the contextual cues in the post in order to generate an accurate prediction.

@@

A model that predicts a user-chosen hashtag is a specific type of the more general recommendation systems.
These systems have grown in need with the growth of the web.
Users on a site need quick access to specific pieces of information, and the site contains much more information than they can process or care about.
Recommendation systems are used to tailor the information presented to what is most relevant to the user \parencite{Pazzani2007}.

@@

Recommendation systems based on the content of user-generated posts have been successful in recommending people on Twitter for a user to follow.
\textcite{Hannon2010} built a Twitter follower recommendation system by creating a profile of each user based on the words they used in previous posts.
The recommendation system would then suggest other Twitter users to follow that had similar profiles to a particular user.
The profiles were created by generating a word frequency matrix of words x (user + followers + followees), and then providing that matrix as input into the Lucine text search engine framework.
When the system needed to recommend a set of individuals for a user to follow, it would take all of the words used in posts from that user to construct a search query to be provided to Lucine.
That search query would return the most likely users that share similar words in posts within their twitter network with the words provided in the query.
Using this simple technique based on a standard text search engine allowed the recommendation system to accurately predict the people that a particular user will follow at 25\% accuracy.

@@

\textcite{Efron2010} showed how hashtags might be used as a type of recommendation system for Twitter.
Users constructed a query of text that represented a search for a topic that they were interested in.
The system then retrieved the most likely hashtags that were associated with that search query.
The model is based on building a word co-occurrence matrix of words x hashtags, and then uses that matrix to assign a similarity score for each hashtag when provided with a search query.
Participants graded how relevant the hashtags returned were to each search query.
The results suggest that hashtags contain useful information that help classify the gist of a post. 
Although this model does not predict hashtags directly when composing a tweet, a model like this could certainly be tailored for that purpose.

@@

\textcite{Kuo2011} was the first to model tag use for StackOverflow posts.
His set of models were originally designed for next-word prediction for large text document collections.
In order to structure the models to work for StackOverflow tag prediction, the models would request the most-likely next word after a user generated a post, and restrict the space of possible words to only tags.
He tested the set of next-word prediction models to generate predictions for the most likely tags that a user would choose when asking a question on the site.
Interestingly, the Bayesian co-occurrence model outperformed the more complicated and computationally expensive Singular Value Decomposition and K-nearest-neighbors models.
This model can accurately predict a user-chosen tag at 47\% accuracy.

\textcite{Stanley2013} also modeled a user's chosen tags for a post on the StackOverflow site.
The model was based on ACT-R's declarative memory retrieval theory, which at the core is also a Bayesian co-occurrence model.
However, this model scaled much better than the co-occurrence model presented in \textcite{Kuo2011}.
Because of this, 100 times more posts were used to build the co-occurrence matrix (\num{1000000} versus \num{10000}), which significantly increased the model's performance.
After scaling up the model, this model can successfully predict a user's tag for a post at 65\% accuracy.
It is interesting that in both research papers the best performing model was based on a Bayesian co-occurrence framework, since that is precisely the framework from which ACT-R's declarative memory system is built.
This suggests that more cognitively-plausible memory retrieval models may outperform more general machine-learning approaches in this particular task domain:
predicting the user-chosen tags for human-generated content on social media sites.

A tag suggestion tool has also been deployed for the \url{http://tex.stackexchange.org} site. \parencite{LatexTags2013}
Both the \LaTeX site and StackOverflow are part of the broader StackExchange network of question and answer sites, and they provide the same user interface and workflow when asking questions.
Once a user has created a question on the Latex site, the site provides subdued text of suggested tags in the text field where the user fills in the tags to associate with the question.
The post author is not forced to use the suggested tags, and is free to choose tags from them or tags not represented in the suggested set.

@@

The hashtag recommendation system deployed for the Google+ microblogging service is probably the most ambitious model of user-created hashtags to date \parencite{GoogleKeynote2013}.
The user interface for this recommendation system for an example Google+ post is shown in Figure \ref{figGoogle+Hashtags}.

\begin{figure}[!htbp]
  \scalebox{.4}{\resizebox{\linewidth}{!}{\includegraphics{google+HashtagExample-crop.pdf}}}
  \caption{Example post on Google+. The system recommended \emph{\#SFGiants} and \emph{\#BusterPosey} as hashtags for the user-generated post}
  \label{figGoogle+Hashtags}
\end{figure}

@@

Several other models have taken a tweet-centered approach to hashtag prediction, where suggested hashtags are collected from hashtags used from similar tweets.
\textcites{Li2011, Zangerle2011, Kywe2012} all store a content vector for each tweet, and then compute a word co-occurrence-based similarity score between a composed tweet and the rest of the tweets in the database.
\textcites{Zangerle2011, Kywe2012} use the Apache Lucine infrastructure to compute the similarity score, while \textcite{Li2011} uses a custom similarity score derived from the WordNet database to compute similarities.
Regardless of the method to compute the similarity between tweets, each method collects the hashtags used from a set of the most similar tweets, then ranks the set, and presents the top 5-10 hashtags to the user.

This tweet-centered approach is quite different than the hashtag-centered approach presented in \textcite{Mazzia2009}.
With a hashtag-centered approach, a direct association is built between the words in a tweet and hashtags that occur in tweets.
With a tweet-centered approach, that association between words and hashtags is indirect:
The relationship is built between a tweet and its content, and then similar tweets are assumed to use similar hashtags.
One problem with the tweet-centered approach is that the storage size grows with the number of tweets, as a vector representation of the content in each tweet has to be maintained to later compute tweet similarity.
The storage size for a hashtag-centered approach grows with the number of hashtags, but it seems reasonable that this will grow slower than the number of tweets and asymptote after collecting a large sample of tweets.
So from the perspective of efficient information storage and retrieval, it seems more likely that the hashtag-centered approach used in \textcite{Mazzia2009} will scale as Twitter grows in size and use.

\textcite{Kywe2012} also customized their tag prediction model to the user's past hashtag use, and was one of the first to do so when developing a hashtag-prediction model for Twitter.
The set of recommended hashtags was the union of hashtags used in similar tweets and hashtags used by similar users.
This was done by storing a content vector of hashtag use for each user (user-centered approach) alongside the content vectors of hashtag use for each tweet (tweet-centered approach).
To generate recommended hashtags, the model would return the top-ranked hashtags from the hashtags used in 0-50 similar tweets and 0-4 similar users.
Prediction accuracy improved when the model combined recommendations based on hashtags in both similar tweets and the top few similar users compared to basing recommendations on similar tweets alone.

A topics-based approach was used by \textcite{Godin2013}, where the model predicted the most likely set of topics that were associated with a tweet, and tested if these topics matched the tweet by using human raters.
The latent topics for the collection of tweets were generated using a Latent Dirichlet Allocation (LDA) statistical methodology.
This is similar to singular value decomposition in that the most likely hidden dimensions (i.e., topics) of the data are discovered by searching for reduced representations of the data that cover most of the variance. 
Human graders rated how well the models generated topics for a tweet related to the content in the tweet.
The LDA model performed well, and generated relevant topics.

@@

Although recent work has been done to model human tagging on the StackOverflow site, to our knowledge no vector-based holographic memory model has been tested or used.
We are curious to see the prediction difference between a vector-based models and current co-occurrence models on the StackOverflow dataset.
Both types of models are neurologically plausible, and both have been successfully incorporated as the declarative memory component of the ACT-R cognitive architecture \parencite{Rutledge2007}. 
Given that the Bayesian cognitively-plausible models have done so well to predict tag use on StackOverflow, we are curious to see how a cognitively-plausible vector-based model performs at the task.

Also, a vector-based retrieval model has not yet been tested on Twitter.
One of the advantages of vector-based models is that word order can be easily incorporated into the single co-occurrence representation \parencite{Jones2007}.
It seems quite likely that the few words used just before a hashtag embedded in a tweet will be highly predictive of the hashtag chosen.
To our knowledge, only bag-of-words models have been tested on Twitter to predict hashtags, where co-occurrence between words and hashtags are computed independently from where the word is located in the tweet.
It will be interesting to see how much (if at all) accuracy improves when incorporating word-order information into the model.

There has been a mix of co-occurrence and latent-based models created to predict hashtags use on Twitter, and the results are encouraging.
However, there has been very little research on how a specific user's past hashtag use should influence the model's prediction when that user is composing a tweet.
\textcite{Kywe2012} did take a user-centered view with their model, but the hashtags predicted by the user and content were analyzed separately and then the top from each group were combined for prediction.
The ACT-R declarative memory retrieval theory shows how past user behavior and current context combine to produce the most likely retrieval.
Each component is summed together to generate a total activation, and then the likelihood of chunks are ranked by that summed activation.
This technique allows for a more natural combination of the two components, where weights can be assigned to each component depending on how strongly each term predicts performance.
This type of weighted additive model that combines past user behavior and current tweet context to predict the most likely hashtags has not yet been explored for Twitter.

@@

ACT-R \parencite{Anderson2004} is a cognitive architecture that formalizes how each cognitive process of the brain (e.g., memory, learning, visual and motor) interacts to produce behavior.
The declarative memory system is a component of that architecture that models the timing, learning, and forgetting processes that make up long-term declarative memory retrieval.
The equations that make up this system can be described through a rational analysis of long-term memory retrieval.
That is, given the task of retrieving a chunk of information from long-term declarative memory,
the current context (i.e., external and internal environment state), and past experience (i.e., prior memories and exposure), 
what is the optimal behavior (i.e., the optimal chunk to retrieve from memory)?
Using Bayesian reasoning, each chunk of information in declarative memory can be assigned a prior likelihood of being retrieved again, given the prior number of times it has been needed.
Those prior probabilities for each chunk are then adjusted for the current context, so that the posterior probabilities represent the likelihood that a chunk is needed, given prior odds and current environment state.

@@

For some domains, it is reasonable to assume that the base-level activations of each chunk within a particular window of interest are stable, and do not change within that window.
Programming-language popularity over the past few years is a reasonable example of this.
Although the popularity of various programming languages has certainly changed slightly over the past few years (e.g., \emph{closure}'s growth), it is not the case that the changes have been drastic.
\emph{C\#}, \emph{Python}, and \emph{Java} are still a few of the most popular languages, \emph{Common Lisp} has not gained or lost much ground in popularity over the past few years, etc.

@@

Strength of association ($S_{ji}$) reflects the amount of log odds adjustment to the activation of a chunk, given the current context (i.e., external environment and internal state).
Context for the StackOverflow domain for example, can be represented as each word in the title and body of a post.
Context for the Twitter domain would be the words in a Tweet.
Association strength between a chunk in memory and a single contextual element can be computed directly by calculating its context-adjusted odds ratio:
The likelihood a chunk occurred with the current context ($p(i|j)$) over the likelihood that the chunk occurred in any of the other contexts ($p(i|\overline{j})$).
For large datasets, the likelihood that a chunk occurs in any particular context reaches near-zero values ($p(j) \Rightarrow 0$).
So it can be assumed that the likelihood that a chunk occurs in any context but one ($p(i|\overline{j})$) is equivalent to the likelihood that a chunk occurs in any context ($p(i)$).
This assumption has been both mentioned and used when deriving the $S_{ji}$ equation \parencite{Anderson1989}, as well as in recent research working with large-scale datasets \parencite{Stanley2013}.

Using this assumption for large datasets, the interpretation of the context-adjusted odds ratio becomes much simpler.
If this ratio for a particular tag and context chunk is greater than one, then the log is positive, which means that this context has been observed more often with this tag than in general.
If this ratio is less than one, then the log is negative, which provides a negative adjustment of total activation since this context has been observed more often in general than with this particular tag.

@@

The majority of tag-recommendation systems use some measure of word pair associations to compute the likelihood of a tag, given current context.
It is important that this measure scales well enough to handle the sheer volume of information present in online social media datasets.
Large-scale social media datasets such as StackOverflow and Twitter contain on the order of millions to hundreds of millions of unique word pair associations between terms and tags.
If one wants to capitalize on all of the information present in the database to build the most accurate measure of relatedness between words and tags, then the association measure used must scale to this large size.

@@

The SNIF-ACT framework is also based on the large-scale version of $S_{ji}$, and scales well when working with a large-scale search query database for internet search \parencites{Fu2007,Pirolli2003}.
The $S_{ji}$ values were based on a 118GB local database of 10 million pages of the Stanford WebBase Project \parencite{Farahat2004}.
So this implementation did not fit into RAM, but a spinning-disk database implementation still scaled well enough for reasonably fast retrieval times for $S_{ji}$ values.

@@

A formal description of the modified ACT-R Bayesian model from \textcite{Stanley2013} is included in Table \ref{tabModACTRModel}.
The activation of each tag ($A_{i}$) is a function of four components:
That tag's base level activation ($B_{i}$), contextual activation for the words in the title, activation for words in the body, and an offset term ($O$).
This model has been modified from the standard ACT-R model (Table \ref{tabACT-RModel}) in three ways:
Two separate contextual components were used (words in title and body of post), an offset term was added, and an entropy metric was used to compute the attentional weight ($W_{j}$).

The offset term was added to normalize the mean activation across retrievals.
This allowed the use of a logistical regression statistical technique to calibrate the weights for each of the terms.
The title and body contextual components were separated since it seemed plausible that the words in the title would be better predictors of the tag used than the words in the body.
It actually turned out that the words in the body were a better predictor of tag use \parencite{Stanley2013}, most likely because there are many more words in the body than the title of the post.
The entropy metric was used to compute the attentional weight for two reasons:
Stop words could be included in the analysis, and more predictive words of some tag (e.g., the word ``PHP'' in a post) were given higher weight.
Using an entropy metric (as opposed to weighting each word equally in the post) allows the model to allocate limited attentional resources ($W$) to important contextual elements.
